(Working Title) Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation?

### 2015-03-12 ms.tex
new stellar table

The full list of stellar parameters adopted in this paper is included in
Table 2.
% For some reason I can't get it to identify the table \ref here.
% If anyone can figure it out, be my guest!

@@

\begin{figure*}[htbp]
\centerline{\includegraphics[width=1.0\textwidth, trim=0 1.5cm 0 1.5cm, clip=true]{f3}}
\caption{Imaging for EPIC 201912552 from 1955 to 2002. There is no background
object directly behind the present day location of the target (red circle) that could be missed 
by the AO observations, while modern SDSS imaging can rule out wide companions
that may have been missed at wide separations, beyond the AO field of view.}
\label{fig:archival}
\end{figure*}

@@

>>>>

The full list of stellar parameters adopted in this paper is included in
Tables 2 and 3. The former lists parameters derived from photometry with
un-inflated uncertainties, while the latter includes this inflating intended to
encapsulate the effect of model uncertainties.
% For some reason I can't get it to identify the table \ref here.
% If anyone can figure it out, be my guest!

@@

\begin{figure*}[htbp]
\centerline{\includegraphics[width=1.0\textwidth, trim=0 1.5cm 0 1.5cm, clip=true]{f3}}
\caption{Imaging for EPIC 201912552 from 1955 to 2002. There is no background
object directly behind the present day location of the target (red circle) that could be missed 
by the AO observations, while modern SDSS imaging can rule out wide companions
that may have been missed at wide separations, beyond the AO field of view. 
All subplots are on the same scale.}
\label{fig:archival}
\end{figure*}

@@

\include{table_stellarprops_inflated}
